Exploring Design Space for Differentially Private Bayesian Inference

### 2018-12-27 ICML2019/main.tex
update algorithms and Accuracy

\noindent \textbf{Related Work.}

@@

\section{Technical Problem Statement and Motivations}
\label{sec_moti}
We are interested in exploring mechanisms for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (Beta, Dirichlet distribution) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.

@@

 \[
\lapmech(\bysinfer, \dataobs) = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \] 
 where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
 \[
 \lapmech(\bysinfer, \dataobs) = \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
 where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model. $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.

@@

\begin{equation*}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation*}

@@

  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}
  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)\\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  \exp
  \big(
  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

@@

  Doing the same transformation in the denominator:
  \begin{equation*}
  \begin{split}
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  \exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
Based on this, we get:$Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.\\

Considering the post-processing (i.e., taking the floor value of $Y$) in $\lapmech$, we have:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t \geq 0$, and\\
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t < 0$.

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$. By applying Hellinger distance in our case, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
when $t \geq 0$, and\\
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
= \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
\end{array}
$$
when $t < 0$.\\

% When $\alpha = \beta$, we also have:
% \begin{align*}
%  Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
% \leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
%   = \quad & Pr[ - t \leq Y < t + 1] \\
%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
%  \end{align*}
Unfolding the Hellinger distance formula($\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$), we get:
\begin{itemize}
  \item[\textbf{case}] \textbf{t is even}\\
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
  = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

@@

  \item[\textbf{case}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 =
  \qquad &
  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
\qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

\end{itemize}

Given $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:

\begin{itemize}
  \item[\textbf{t = 0}] $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.
  \item[\textbf{t = 1}]
  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$. 
  \item[\textbf{t = 2}]$\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.
\end{itemize}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

By solving following equations:
\begin{itemize}
  \item
\[
\frac{1}{\nomalizer{\dataobs}} = 0.19673467014\ or\ 0.31606027941
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer.

  \item 
\[
\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
 = 0.11932560927\ or\ 0.11627207896
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.

>>>>

@@

\section{Problem Statement}
\label{sec_moti}
We are interested in exploring mechanisms for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (Beta, Dirichlet distribution) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.

@@

 \[
\lapmech(\bysinfer, \dataobs) = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \] 
 where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
 \begin{equation*}
 \begin{split}
 & \lapmech(\bysinfer, \dataobs) = \\
 & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \end{split}
 \end{equation*}
 where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model. $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.

@@

\begin{equation*}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation*}

@@

  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \\
  & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}
  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)\\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

@@

  Doing the same transformation in the denominator:
  \begin{equation*}
  \begin{split}
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \\
  & \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)}\\
  & \cdot\frac{1}{
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)}\\
  & \cdot \frac{1}{
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
Based on this, we get:$Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.

Considering the post-processing (i.e., taking the floor value of $Y$) in $\lapmech$, we have:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t \geq 0$, and
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t < 0$.

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$. By applying Hellinger distance in our case, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
when $t \geq 0$, and\\
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
\end{array}
$$
when $t < 0$.\\

% When $\alpha = \beta$, we also have:
% \begin{align*}
%  Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
% \leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
%   = \quad & Pr[ - t \leq Y < t + 1] \\
%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
%  \end{align*}
Unfolding the Hellinger distance formula, we get:\\
  \noindent \textbf{case: t is even}\\
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 \\
  & = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

@@

  \noindent \textbf{case: t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
  & Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \\
  & =
  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
\qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:

  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.

  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.

  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.

In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

By solving following equations:
\begin{itemize}
  \item
\[
\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer.
